Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-19 paper/v2/paper-edited.tex
balance last page
minor edit in section 6

Constructing automata for extended regular expressions (i.e., regular expressions with negation and intersection operations) is known to have high complexity~\cite{regex-complexity}. The \sysname compiler uses regular expressions derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions over large alphabets efficiently. Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy. Similarly, to model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.
%
Rather than construct the product graph in full, our implementation prevents exploring parts of the graph when no accepting state is reachable in any of the corresponding regular automata during construction.

@@

@@

>>>>

Constructing automata for extended regular expressions (i.e., regular expressions with negation and intersection operations) is known to have high complexity~\cite{regex-complexity}. The \sysname compiler uses regular expressions derivatives~\cite{regex-derivatives} with character classes to construct deterministic automata for extended regular expressions efficiently. Since regular expressions are defined over a finite alphabet, and since much of the AS topology is unknown, we set the alphabet to include all uniquely referenced external ASes in the policy. To model the unknown external AS topology beyond immediate peers, we include a special topology node to represent any unknown location.
%
Rather than construct the product graph in full, our implementation prevents exploring parts of the graph during construction when no automata has a reachable accepting state.

@@

\section*{Acknowledgement}

\ryan{TODO: add acknowledgements}

@@

\balance
